---
title: "Statistics for the CogSci article 'Cooperation and deception in the Mod-Signal Game'"
author: "Abi Raveenthiran, J.D. Top"
date: '6-11-2024'
output: html_document
---

Package loading
```{r setup, include=FALSE}
library(magrittr)
library(dplyr)
library(hash) 
library(purrr)
```

Comparison of confidence that humans are human and agents are human as reported in the final questionnaire
```{r}
q_data <- read.csv('modsignal_questionnaire_data.csv', na.strings= c("-"))  # Read questionnaire data

# Make separate datasets for each of the three player numbers
data_p1 <- q_data %>% filter(grepl("1$", Participant))
data_p2 <- q_data %>% filter(grepl("2$", Participant))
data_p3 <- q_data %>% filter(grepl("3$", Participant))

# Vectors with each participant's mean confidence that the humans they played against were human, and the agent they played against was human
confidenceHumanVector = c()
confidenceAgentVector = c()

for(i in 1:21) {
  if(grepl("1$", q_data$Participant[i])){
    confidenceHumanVector = c(confidenceHumanVector, mean(c(q_data$B1.Human..[i], q_data$B2.Human..[i])))
    confidenceAgentVector = c(confidenceAgentVector, q_data$B3.Human..[i])
  } else if(grepl("2$", q_data$Participant[i])) {
    confidenceHumanVector = c(confidenceHumanVector, mean(c(q_data$B1.Human..[i], q_data$B3.Human..[i])))
    confidenceAgentVector = c(confidenceAgentVector, q_data$B2.Human..[i])
  } else if(grepl("3$", q_data$Participant[i])) {
    confidenceHumanVector = c(confidenceHumanVector, mean(c(q_data$B2.Human..[i], q_data$B3.Human..[i])))
    confidenceAgentVector = c(confidenceAgentVector, q_data$B1.Human..[i])
  }
}

# Means and SDs
mean(confidenceHumanVector[!is.na(confidenceHumanVector)])
sd(confidenceHumanVector[!is.na(confidenceHumanVector)])
mean(confidenceAgentVector[!is.na(confidenceAgentVector)])
sd(confidenceAgentVector[!is.na(confidenceAgentVector)])

# First we test for normality
qqnorm(confidenceHumanVector[!is.na(confidenceHumanVector)])
shapiro.test(confidenceHumanVector[!is.na(confidenceHumanVector)])
qqnorm(confidenceAgentVector[!is.na(confidenceAgentVector)])
shapiro.test(confidenceAgentVector[!is.na(confidenceAgentVector)])

# T-Test comparing confidence in human being human and agents being human
t.test(confidenceHumanVector, confidenceAgentVector, paired = TRUE, alternative = "two.sided", na.rm=TRUE)

```


Compare distance to signal between humans in the human-human condition, humans in the human-agent condition, and the agent in the human-agent condition.

Distance between choice and signal

If c is your choice, and s is the signal, then the distance 
between your choice and the signal is min{(c − s) mod 24, (s − c) mod 24}. 
For human players, the mean was around 3.5. As there is no
signal in the Mod game, Frey and Goldstone (2013) use the
distance between players’ choices, the mean of which was
3.6. For perfect cooperative play in the Mod-Signal game,
the mean distance between choice and signal would be
0.5. In the Mod game, the mean distance between choices
would be 1 for perfect cooperation. For both metrics, the
mean for random play would be around 6.
```{r}

data <- read.csv('modsignal_trials_data.csv') # Read  data from file

# First, sort by game and round
# Next, increase signal/action by 1 so it's in range 1-24
adjustedData <- data[order(data$game,data$round ),] %>% mutate(signal = signal+1, action = action+1)
adjustedData <- adjustedData %>% filter(!grepl("(s5_g23|s5_g24|s5_14|s5_24)", game))  # Exclusions: Remove two games, as well as two weird datapoints

# Separate data into signaler and responder data
signals <- adjustedData %>% filter(round%%2 == player%%2)
responses <- adjustedData %>% filter(round%%2 != player%%2)
signals <- signals %>% rename(signaler = player, actionTime = reactionTime)
responses <- responses %>% rename(responder = player, response = action)

# Merge signaler and responder data
mergedData <- merge(signals, responses, by = c("game", "round", "signal"))

# Separate data by game
mergedGames <- group_split(mergedData, mergedData$game)

# Add distance from choices to signal and responses to signal
mergedData <- mergedData %>% mutate(
  actionAbsDiff = case_when(
    abs((action-1) - (signal-1)) > 12 ~ 24 - abs((action-1) - (signal-1)),
    abs((action-1) - (signal-1)) <= 12 ~ abs((action-1) - (signal-1)) 
  ),
  responseAbsDiff = case_when(
    abs((response-1) - (signal-1)) > 12 ~ 24 - abs((response-1) - (signal-1)),
    abs((response-1) - (signal-1)) <= 12 ~ abs((response-1) - (signal-1)) 
  )
)

# Add distance to signal for each player
mergedData <- mergedData %>% mutate(
  player1AbsDiff = case_when(
    round%%2 == 1 ~ actionAbsDiff, 
    round%%2 == 0 ~ responseAbsDiff
  ),
  player0AbsDiff = case_when(
    round%%2 == 0 ~ actionAbsDiff, 
    round%%2 == 1 ~ responseAbsDiff
  )
)

# Separate data by game
mergedGames <- group_split(mergedData, mergedData$game)

# Compute distance to signal
sigDistHH = c()
sigDistHA = c()
sigDistA = c()

for (game in mergedGames){
  if(!grepl("4$", head(game$game, 1))){
    player0sigDist = game$player0AbsDiff
    player1sigDist = game$player1AbsDiff
    sigDistHH <- c(sigDistHH, player0sigDist)
    sigDistHH <- c(sigDistHH, player1sigDist)
  } else if(grepl("4$", head(game$game, 1))){
    player0sigDist = game$player0AbsDiff
    sigDistHA <- c(sigDistHA, player0sigDist)
    
    player1sigDist = game$player1AbsDiff
    sigDistA <- c(sigDistA, player1sigDist)
  }
}

# Convert to data frame
sigDistFrameHA = data.frame(sigDistHA, seq(1:length(sigDistHA)))
sigDistFrameHH = data.frame(sigDistHH, seq(1:length(sigDistHH)))
sigDistFrameA = data.frame(sigDistA, seq(1:length(sigDistA)))

# Compute means and SDs
mean(sigDistFrameHH$sigDistHH)
sd(sigDistFrameHH$sigDistHH)
mean(sigDistFrameHA$sigDistHA)
sd(sigDistFrameHA$sigDistHA)
mean(sigDistFrameA$sigDistA)
sd(sigDistFrameA$sigDistA)

# Check for normality
qqnorm(sigDistHH)
shapiro.test(sigDistHH)
qqnorm(sigDistHA)
shapiro.test(sigDistHA)
qqnorm(sigDistA)
shapiro.test(sigDistA)

# Run a Kruskal-Wallis test
res <- kruskal.test(list(sigDistHH,sigDistHA,sigDistA))
res
```

Compare efficiency, or number of rounds where a point was gained
```{r}

# Add both players' points to data
mergedData <- mergedData[order(mergedData$game, mergedData$round),] %>% mutate(
  player1Point = case_when(
    action-response == 1 & round%%2 == 1 ~ 1, 
    action-response == -23 & round%%2 == 1 ~ 1, 
    action-response != (-23 && 1) & round%%2 == 1 ~ 0,
    response-action == 1 & round%%2 == 0 ~ 1,
    response-action == -23 & round%%2 == 0 ~ 1,
    response-action != (-23 && 1) & round%%2 == 0 ~ 0),
  player0Point = case_when(
    action-response == 1 & round%%2 == 0 ~ 1, 
    action-response == -23 & round%%2 == 0 ~ 1, 
    action-response != (-23 && 1) & round%%2 == 0 ~ 0,
    response-action == 1 & round%%2 == 1 ~ 1,
    response-action == -23 & round%%2 == 1 ~ 1,
    response-action != (-23 && 1) & round%%2 == 1 ~ 0)
  )

# Separate data by game
mergedGames <- group_split(mergedData, mergedData$game)

# Compute scores
scoresHA = c()
scoresHH = c()
scoresA = c()  # NEW

for (game in mergedGames){
  if(!grepl("4$", head(game$game, 1))){
    player1Points = sum(game$player1Point)
    player0Points = sum(game$player0Point)
    scoresHH <- c(scoresHH, player0Points)
    scoresHH <- c(scoresHH, player1Points)
  } else if(grepl("4$", head(game$game, 1))){
    player0Points = sum(game$player0Point)
    scoresHA <- c(scoresHA, player0Points)
    
    player1Points = sum(game$player1Point)  # NEW for agent
    scoresA <- c(scoresA, player1Points)
  }
}

# Calculate proportions and efficiency
sum(scoresHH)
length(scoresHH)*20
sum(scoresHH)/(length(scoresHH)*20)
sum(scoresHA)
length(scoresHA)*20
sum(scoresHA)/(length(scoresHA)*20)
sum(scoresA)
length(scoresA)*20
sum(scoresA)/(length(scoresA)*20)


# Run Chi-squared test
tab <- as.table(rbind(c(sum(scoresHH),sum(scoresHA),sum(scoresA)),c((length(scoresHH)*20)-sum(scoresHH), (length(scoresHA)*20)-sum(scoresHA), (length(scoresA)*20)-sum(scoresA))))
dimnames(tab) <- list(point = c("yes","no"), player = c("HH","HA","A"))
xsq <- chisq.test(tab)
xsq

(sum(scoresHH)+sum(scoresHA))/(length(scoresHH)*20 + length(scoresHA)*20)  # Mean efficiency across both conditions
```

Signals, rates, accelerations for generating the circular histograms
```{r}

# Add difference between signal and action, and remove agent plays
signals <- signals %>% mutate(diff = case_when(
  action-signal <= -1 ~ (action-signal+24),
  action-signal >= 0 ~ (action-signal+0))) %>% filter(signaler!=3)

responses <- responses %>% mutate(diff = case_when(
  response-signal <= -1 ~ (response-signal+24),
  response-signal >= 0 ~ (response-signal+0))) %>% filter(responder!=3)

# Function for circular shifting of data
circshift_any <- function(a, sz) {
  indexers <- map2(dim(a), sz, function(len, s) (1:len - s - 1) %% len + 1)
  indexing_matrix <- as.matrix(do.call(expand.grid, indexers))

  array(a[indexing_matrix], dim(a))
}

dataLine1 <- toString(table(factor(signals$diff, levels = 0:23)))  # Frequencies of choice-signal differences as string
dataLine2 <- toString(table(factor(responses$diff, levels = 0:23))) 
dataLabel1 <- toString(c(seq(12,0,-1),seq(23,13,-1)))
dataLabel2 <- dataLabel1
dataCaptions <- "Choice - Signal signaler,Choice - Signal receiver,Acceleration"

# Now compute acceleration
# Remove agent data and add difference
humanData <- adjustedData %>%  filter(player!=3) %>% mutate(diff = case_when( #  
  action-signal <= -1 ~ (action-signal+24),
  action-signal >= 0 ~ (action-signal+0)))
humanData <- arrange(humanData, game, round, player) # Sort so player 0 is odd and player 1 is even rows

# Add cooperative difference
humanData <- humanData %>% mutate(coopdiff = case_when(
  round%%2 == player%%2 ~ diff,   # Signal
  round%%2 != player%%2 ~ (diff - 1) %% 24 # Response
))

# Calculate acceleration
humanData <- humanData %>% mutate(acc = case_when(
  round == 1 ~ NA,
  round != 1 ~ (coopdiff - lag(coopdiff,2))
))

# Remove NAs
humanData <- humanData %>% mutate(acc = acc %% 24)

totData <- humanData %>% filter(!is.na(acc))                                        # All data
hhData <- humanData %>% filter(substr(game, 6, 6) != "4") %>% filter(!is.na(acc))   # Remove all rounds with computer
haData <- humanData %>% filter(substr(game, 6, 6) == "4") %>% filter(!is.na(acc))   # Remove all rounds without computer

# Separate into cooperative and competitive data
coopDat <- humanData %>% filter(coopdiff == 0) %>% filter(!is.na(acc)) 
compDat <- humanData %>% filter(coopdiff != 0)

# Generate graphs as string
dataLine3 <- toString(table(factor(totData$acc, levels = 0:23)))
dataLabel3 <- dataLabel1


outDat <- c(dataLine1,dataLine2,dataLine3,dataLabel1,dataLabel2,dataLabel3,dataCaptions)
file <- file("circlehistogram_data_all.csv")
writeLines(outDat, file)
close(file)

table(factor(signals$diff, levels = 0:23))[1] + table(factor(responses$diff, levels = 0:23))[2] # Total cooperative plays
(sum(table(factor(signals$diff, levels = 0:23))) + sum(table(factor(responses$diff, levels = 0:23)))) - (table(factor(signals$diff, levels = 0:23))[1] + table(factor(responses$diff, levels = 0:23))[2])  # Total non-cooperative plays
table(factor(responses$diff, levels = 0:23))[24] # Playing signal - 1 as responder
table(factor(responses$diff, levels = 0:23))[2]  # Playing signal + 1 as responder

```

Comparing honesty and trust levels
```{r}

# Compute honesty and trust
signals <- signals %>% mutate(honesty = case_when(diff == 0 ~ 1, diff != 0 ~ 0))
responses <- responses %>% mutate(trust = case_when(diff == 1 ~ 1, diff != 1 ~ 0))

# Separate by condition
signalsHH <- signals %>% filter(!grepl("4$", game))
signalsHA <- signals %>% filter(grepl("4$", game))
signalsA <- adjustedData %>% filter(round%%2 == player%%2) %>% rename(signaler = player, actionTime = reactionTime) %>% mutate(diff = case_when(
  action-signal <= -1 ~ (action-signal+24),
  action-signal >= 0 ~ (action-signal+0))) %>% filter(signaler==3) %>% mutate(honesty = case_when(diff == 0 ~ 1, diff != 0 ~ 0))
responsesHH <- responses %>% filter(!grepl("4$", game))
responsesHA <- responses %>% filter(grepl("4$", game))
responsesA <- adjustedData  %>% filter(round%%2 != player%%2) %>% rename(responder = player, response = action) %>% mutate(diff = case_when(
  response-signal <= -1 ~ (response-signal+24),
  response-signal >= 0 ~ (response-signal+0))) %>% filter(responder==3) %>% mutate(trust = case_when(diff == 1 ~ 1, diff != 1 ~ 0))

# Calculate proportions of honesty
h_props <- rbind(c(sum(signalsHH$honesty),sum(signalsHA$honesty),sum(signalsA$honesty)))
h_tots <- c(sum(signalsHH$honesty),sum(signalsHA$honesty),sum(signalsA$honesty))+c(length(signalsHH$honesty)-sum(signalsHH$honesty), length(signalsHA$honesty)-sum(signalsHA$honesty), length(signalsA$honesty)-sum(signalsA$honesty))
h_props[1]/h_tots[1]
h_props[2]/h_tots[2]
h_props[3]/h_tots[3]

# Run a Chi-Squared test on honesty
tab <- as.table(rbind(c(sum(signalsHH$honesty),sum(signalsHA$honesty),sum(signalsA$honesty)),
                      c(length(signalsHH$honesty)-sum(signalsHH$honesty), length(signalsHA$honesty)-sum(signalsHA$honesty), length(signalsA$honesty)-sum(signalsA$honesty))))
dimnames(tab) <- list(honest = c("yes","no"), player = c("HH","HA","A"))
xsq <- chisq.test(tab)
xsq

# Calculate proportions of trust
t_props <- c(sum(responsesHH$trust),sum(responsesHA$trust),sum(responsesA$trust))
t_tots <- c(sum(responsesHH$trust),sum(responsesHA$trust),sum(responsesA$trust))+c(length(responsesHH$trust)-sum(responsesHH$trust), length(responsesHA$trust)-sum(responsesHA$trust), length(responsesA$trust)-sum(responsesA$trust))
t_props[1]/t_tots[1]
t_props[2]/t_tots[2]
t_props[3]/t_tots[3]

# Run Chi-Squared test on trust
tab <- as.table(rbind(c(sum(responsesHH$trust),sum(responsesHA$trust),sum(responsesA$trust)),
                      c(length(responsesHH$trust)-sum(responsesHH$trust), length(responsesHA$trust)-sum(responsesHA$trust), length(responsesA$trust)-sum(responsesA$trust))))
dimnames(tab) <- list(trusting = c("yes","no"), player = c("HH","HA","A"))
xsq <- chisq.test(tab)
xsq

# Make boxplot

signalsListHH <- group_split(signalsHH, signalsHH$game)
signalsListHA <- group_split(signalsHA, signalsHA$game)

honestyVectorHH <- c()
honestyGamesHH <- c()

for (game in signalsListHH){
  honestySumHH = sum(game$honesty)/20*100
  honestyVectorHH <- c(honestyVectorHH, honestySumHH)
  honestyGamesHH <- c(honestyGamesHH, head(game$game, 1))
}
honestyFrameHH = data.frame(honestyVectorHH, honestyGamesHH)

honestyVectorHA <- c()
honestyGamesHA <- c()

for (game in signalsListHA){
  honestySumHA = sum(game$honesty)/10*100
  honestyVectorHA <- c(honestyVectorHA, honestySumHA)
  honestyGamesHA <- c(honestyGamesHA, head(game$game, 1))
}
honestyFrameHA = data.frame(honestyVectorHA, honestyGamesHA)

responsesListHH <- group_split(responsesHH, responsesHH$game)
responsesListHA <- group_split(responsesHA, responsesHA$game)

trustVectorHH <- c()
trustGamesHH <- c()
for (game in responsesListHH){
  trustSumHH = sum(game$trust)/20*100
  trustVectorHH <- c(trustVectorHH, trustSumHH)
  trustGamesHH <- c(trustGamesHH, head(game$game, 1))
}
trustFrameHH = data.frame(trustVectorHH, trustGamesHH)

trustVectorHA <- c()
trustGamesHA <- c()
for (game in responsesListHA){
  trustSumHA = sum(game$trust)/10*100
  trustVectorHA <- c(trustVectorHA, trustSumHA)
  trustGamesHA <- c(trustGamesHA, head(game$game, 1))
}
trustFrameHA = data.frame(trustVectorHA, trustGamesHA)

par(mai = c(1, 1.5, 1, 1))
boxplot(c(trustFrameHH$trustVectorHH,trustFrameHA$trustVectorHA),c(honestyFrameHH$honestyVectorHH,honestyFrameHA$honestyVectorHA),   # NEW: Added agent here
        main = "Honesty/trust levels of humans in all conditions",
        at = c(1,2),  # NEW: added 3
        names = c("Trust","Honesty"),  # NEW: added , "A"
        las = 1,
        col = c("grey", "grey", "grey", "grey", "grey"),
        border = "black",
        horizontal = TRUE,
        notch = FALSE,
        xlab = "Honesty and trust levels (%)",
        ylim = c(0, 100),
        cex.main=2, 
        cex.lab=2,
        cex.axis=2
        
)
```

Compare reaction times for cooperative and non-cooperative play
```{r}

# Add participant numbers
signals <- signals %>% mutate(participant = case_when(
  strtoi(substr(signals$game,6,6)) == 4 & signaler == 1 ~ 0,
  strtoi(substr(signals$game,6,6)) == 4 & signaler == 0 ~ 
    (strtoi(substr(signals$game,2,2))-1)*3 + strtoi(substr(signals$game,5,5)),
  strtoi(substr(signals$game,6,6)) - strtoi(substr(signals$game,5,5)) == 1 & signaler == 1 ~ 
    (strtoi(substr(signals$game,2,2))-1)*3 + strtoi(substr(signals$game,6,6)),
  strtoi(substr(signals$game,6,6)) - strtoi(substr(signals$game,5,5)) == 1 & signaler == 0 ~ 
    (strtoi(substr(signals$game,2,2))-1)*3 + strtoi(substr(signals$game,5,5)),
  strtoi(substr(signals$game,6,6)) - strtoi(substr(signals$game,5,5)) == 2 & signaler == 1 ~ 
    (strtoi(substr(signals$game,2,2))-1)*3 + strtoi(substr(signals$game,5,5)),
  strtoi(substr(signals$game,6,6)) - strtoi(substr(signals$game,5,5)) == 2 & signaler == 0 ~ 
    (strtoi(substr(signals$game,2,2))-1)*3 + strtoi(substr(signals$game,6,6)),
))

responses <- responses %>% mutate(participant = case_when(
  strtoi(substr(responses$game,6,6)) == 4 & responder == 1 ~ 0,
  strtoi(substr(responses$game,6,6)) == 4 & responder == 0 ~ 
    (strtoi(substr(responses$game,2,2))-1)*3 + strtoi(substr(responses$game,5,5)),
  strtoi(substr(responses$game,6,6)) - strtoi(substr(responses$game,5,5)) == 1 & responder == 1 ~ 
    (strtoi(substr(responses$game,2,2))-1)*3 + strtoi(substr(responses$game,6,6)),
  strtoi(substr(responses$game,6,6)) - strtoi(substr(responses$game,5,5)) == 1 & responder == 0 ~ 
    (strtoi(substr(responses$game,2,2))-1)*3 + strtoi(substr(responses$game,5,5)),
  strtoi(substr(responses$game,6,6)) - strtoi(substr(responses$game,5,5)) == 2 & responder == 1 ~ 
    (strtoi(substr(responses$game,2,2))-1)*3 + strtoi(substr(responses$game,5,5)),
  strtoi(substr(responses$game,6,6)) - strtoi(substr(responses$game,5,5)) == 2 & responder == 0 ~ 
    (strtoi(substr(responses$game,2,2))-1)*3 + strtoi(substr(responses$game,6,6)),
))

# Create cooperative/non-cooperative data
honestSignals <- signals %>% filter(honesty == 1) %>% rename(player = signaler, reactionTime = actionTime) %>% mutate(trust = -1)
disHonestSignals <- signals %>% filter(honesty == 0) %>% rename(player = signaler, reactionTime = actionTime) %>% mutate(trust = -1)
trustingResponses <- responses %>% filter(trust == 1) %>% rename(player = responder, action = response) %>% mutate(honesty = -1)
disTrustingResponses <- responses %>% filter(trust == 0) %>% rename(player = responder, action = response) %>% mutate(honesty = -1)

coopPlays <- rbind(honestSignals,trustingResponses)    
noncoopPlays <- rbind(disHonestSignals,disTrustingResponses)

# Make list of cooperative and non-cooperative reaction times
meansCoopRT = c()
meansNoncoopRT = c()
for(i in 1:21){
  meansCoopRT = c(meansCoopRT, (mean(log(coopPlays$reactionTime[coopPlays$participant == i]))))
  meansNoncoopRT = c(meansNoncoopRT, (mean(log(noncoopPlays$reactionTime[noncoopPlays$participant == i]))))
}

# Calculate means and SDs
mean(meansCoopRT[!is.na(meansCoopRT)])
sd(meansCoopRT[!is.na(meansCoopRT)])
mean(meansNoncoopRT[!is.na(meansNoncoopRT)])
sd(meansNoncoopRT[!is.na(meansNoncoopRT)])

# Check for normality
qqnorm(meansCoopRT)
shapiro.test(meansCoopRT)
qqnorm(meansNoncoopRT)
shapiro.test(meansNoncoopRT)

# Run t-test
t.test(meansCoopRT, meansNoncoopRT, paired = TRUE, alternative = "two.sided", na.rm=TRUE)
```

First rounds of deception in the human-human games
```{r}

# Add column for whether any deception occurs (here, as responder, signal - 1 is cooperative)
mergedData <- mergedData %>%  mutate(honesty = case_when(actionAbsDiff == 0 ~ 1, actionAbsDiff != 0 ~ 0)) %>%  mutate(trust = case_when(responseAbsDiff == 1 ~ 1, responseAbsDiff != 1 ~ 0)) %>% mutate(sacrif = case_when((responseAbsDiff %% 24) == 23 ~ 1,  (responseAbsDiff %% 24) != 23 ~ 0)) %>% mutate(coop = trust + sacrif) %>% mutate( anydecep = 1-(honesty*coop))

mergedDataHH <- mergedData %>% filter(!grepl("4$", game))  # Only the human-human condition

gameDict <- hash()
for( i in rownames(mergedDataHH) ){
  gameName <- mergedDataHH[i, "game"]
  gameDict[[gameName]] <- 9001
}
for( i in rownames(mergedDataHH) ){
  gameName <- mergedDataHH[i, "game"]
  roundNum <- mergedDataHH[i, "round"]
  decep <- mergedDataHH[i, "anydecep"]
  if(decep == 1){
    if( roundNum < gameDict[[gameName]]){
      gameDict[[gameName]] <- roundNum
    }
  }
}
table(values(gameDict))  # First deception in the human-human condition
```

Who played non-cooperatively first in the human-agent condition?
```{r}

mergedDataHA <- mergedData %>% filter(grepl("4$", game))  # Only the human-agent condition

# First store first round of non-cooperation for each game
firstDict <- hash()
for( i in rownames(mergedDataHA) ){
  gameName <- mergedDataHA[i, "game"]
  firstDict[[gameName]] <- 9001
}

for( i in rownames(mergedDataHA) ){
  gameName <- mergedDataHA[i, "game"]
  roundNum <- mergedDataHA[i, "round"]
  decep <- mergedDataHA[i, "anydecep"]
  if(decep == 1){
    if( roundNum < firstDict[[gameName]]){
      firstDict[[gameName]] <- roundNum
    }
  }
}
humanFirst = 0
# Now loop over games to count who shot first
for (key in ls(firstDict)) {
  fullRound = mergedData[mergedData$game==key & mergedData$round==firstDict[[key]],]
  print(fullRound)
  if(fullRound$signaler == 3){  # IF agent signals
    if(fullRound$coop == 0){
      humanFirst <- humanFirst + 1
    }
  } else {
    if(fullRound$honesty == 0){
      humanFirst <- humanFirst + 1
    }
  }
}
humanFirst

```

How often does the agent suffer from its bug?
```{r}

# Count how often agent does not cooperate
nonCoop = 0
bug = 0
tot = 0
for(i in rownames(mergedDataHA)){
  tot <- tot + 1
  if(mergedDataHA[i,"signaler"] == 3){  # Agent is signaling
    if(mergedDataHA[i,"honesty"] == 0){
       nonCoop <- nonCoop + 1
       if(i != 0){
          lastSignal = mergedDataHA[as.numeric(i)-1,"signal"]
          lastAction = mergedDataHA[as.numeric(i)-1,"action"]
          if(lastSignal > lastAction){
            bug <- bug + 1
          }
       }
    }
  } else {
    if(mergedDataHA[i,"trust"] == 0){
       nonCoop <- nonCoop + 1
       if(i != 0){
          lastSignal = mergedDataHA[as.numeric(i)-1,"signal"]
          lastResponse = mergedDataHA[as.numeric(i)-1,"response"]
          if(lastSignal > lastResponse){
            bug <- bug + 1
          }
       }
    }    
  }
}
bug
```

Is there a correlation between higher-order iterated reasoning and longer log-RTs?

```{r}

# Add log-RTs to data
signals <- signals %>%  mutate(logRT = log(actionTime))
responses <- responses %>%  mutate(logRT = log(reactionTime))

# Remove expected plays
signalsno0 <- signals %>% filter(diff!=0)
responsesno0 <- responses %>% filter(diff!=1)

### Combine data
cutSig <- signalsno0[c(6,7,10)]
cutRes <- responsesno0[c(6,7,10)]
names(cutSig)[names(cutSig) == 'actionTime'] <- 'RT'
names(cutRes)[names(cutRes) == 'reactionTime'] <- 'RT'
cutSig$id <- 1:nrow(cutSig)
cutRes$id <- (nrow(cutSig)+1):(nrow(cutSig)+nrow(cutRes))
totRTs <- Reduce(function(x, y) merge(x, y, all=TRUE), list(cutSig,cutRes)) 
totRTs_sub6 <- totRTs %>%  filter(diff < 7)

# Correlation
cor(totRTs_sub6$logRT,totRTs_sub6$diff, method="spearman")
cor.test(totRTs_sub6$logRT,totRTs_sub6$diff,method="spearman")
```
